Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-04 paper/SI.tex
Minor revision in main and SI

\begin{table}[htbp]
  \centering
  \begin{tabular}{lcc}
    \hline
    Solution & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm) \\
    \hline
    0.1 mM NaCl	&0.018	&30.4\\
    0.1 mM LiCl	&0.0158	&30.4\\
    0.1 mM CaCl$_{2}$&	0.02187	&17.2\\
    0.1 mM MgSO$_{4}$	&0.0327	&15.2\\
    0.1 mM K$_{2}$SO$_{4}$	&0.0416	&17.2\\
    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&9.6\\
    \hline
  \end{tabular}
  \caption{conductivity}
  \label{tab:conductivity}
\end{table}

>>>>

\begin{table}[htbp]
  \centering
  \begin{tabular}{lcc}
    \hline
    Solution & Conductivity (mS$\cdot$cm$^{-1}$) & $\lambda_{\mathrm{D}}$ (nm) \\
    \hline
    0.1 mM NaCl	&0.018	&30.4\\
    0.1 mM LiCl	&0.0158	&30.4\\
    0.1 mM CaCl$_{2}$&	0.02187	&17.2\\
    0.1 mM MgSO$_{4}$	&0.0327	&15.2\\
    0.1 mM K$_{2}$SO$_{4}$	&0.0416	&17.2\\
    0.1 mM K$_{3}$(Fe(CN)$_{6}$)&	0.0595	&12.4\\
    \hline
  \end{tabular}
  \caption{conductivity}
  \label{tab:conductivity}
\end{table}

### 2018-10-04 paper/paper.tex
Minor revision in main and SI

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

@@

\title{Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene}

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  Atomically thin graphene nanopores is emerging as one of the most
  promising candidates for next-generation membrane technology owing
  to the ultrahigh permeability. However, the size-exclusive mechanism
  limits its scalability as it remains technically challenging to
  drill subnanometer pores over a large area. Here we report
  macroscopic salt rejection through monolayer porous graphene with
  the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
  limitation set by the hydrated radii. By electrostatically gating a
  sheet of porous graphene, we report a considerable reduction of salt
  flux by up to 55\% with the gate voltage. We systematically
  investigate the effects of salt concentration and species, including
  developing a theory to model the electrolyte diffusion through a
  nanopore in a sheet of gated monolayer graphene. The interplay
  between graphene quantum capacitance and electrical double layer is
  identified to be the main mechanism responsible for the observed
  salt rejection, when the pore size is comparable to the Debye
  screening length. Our findings reveal a new degree of freedom
  controlling the membrane potential and electrolyte permeation
  through porous two-dimensional monolayers.
\end{abstract}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the effects of
external concentration polarization, and a conductivity probe is
placed in the LCR to monitor the ionic concentration as a function of
time. The membrane is attached to a piece of copper tape connected to
a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
the LCR grounded (\Fig{} \ref{fig:1}a inset). We fabricated the
PCTE-supported PG using the protocol developed by our group
\cite{Choi_2018}, as schematically shown in \Fig{} \ref{fig:1}b. The
normally distributed, circular pores with pore diameters of 20$\pm$10
nm (\Fig{} \ref{fig:1}c inset) over a large area were drilled on
graphene.  By optimizing the subsequent transfer process, a high
surface coverage ($>$ 98\%) of graphene on PCTE was reached (\Fig{}
\ref{fig:1}c), allowing to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1).  The
system presented here allows us to systematically investigate the
diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
driven by the gradient of electrochemical potential in the electrolyte
medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
duration (1 h), suggesting the concentration change in individual
reservoirs is negligible \todo[inline]{Isn't the increasing of
  conductivity a measure of the diffusion of ions?}. The diffusive fluxes
correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
\Fig{} \ref{fig:2}b and Supplementary \Fig{} S2). For comparison
purposes, based on the assumption that the membrane consists
cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through the
bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table S1), the
calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
reasonable agreement with the experimental values.

>>>>

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
\newcommand{\hide}[1]{}
% \usepackage{lineno}
% \linenumbers

@@

\title{Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene}

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  Atomically thin graphene nanopores is emerging as one of the most
  promising candidates for next-generation membrane technology owing
  to the ultrahigh permeability. However, the size-exclusive mechanism
  limits its scalability as it remains technically challenging to
  drill subnanometer pores over a large area. Here we report
  macroscopic salt rejection through  porous graphene with
  the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
  limitation set by the hydrated radii. By electrostatically gating a
  sheet of porous graphene, we report a considerable reduction of salt
  flux by up to 55\% with the gate voltage. We systematically
  investigate the effects of salt concentration and species, including
  developing a theory to model the electrolyte diffusion through a
  nanopore in a sheet of gated  graphene. The interplay
  between graphene quantum capacitance and electrical double layer is
  identified to be the main mechanism responsible for the observed
  salt rejection, when the pore size is comparable to the Debye
  screening length. Our findings reveal a new degree of freedom
  controlling the membrane potential and electrolyte permeation
  through porous two-dimensional materials.
\end{abstract}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the effects of
external concentration polarization, and a conductivity probe is
placed in the LCR to monitor the ionic concentration as a function of
time. The membrane is attached to a piece of copper tape connected to
a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
the LCR grounded (\Fig{} \ref{fig:1}a inset). We fabricated the
PCTE-supported PG using the protocol developed by our group
\cite{Choi_2018}, as schematically shown in \Fig{} \ref{fig:1}b. The
normally distributed, circular pores with pore diameters of 20$\pm$10
nm (\Fig{} \ref{fig:1}c inset) over a large area were drilled on
graphene.  By optimizing the subsequent transfer process, a high
surface coverage ($>$ 98\%) of graphene on PCTE was reached (\Fig{}
\ref{fig:1}c), allowing to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1).  The
system presented here allows us to systematically investigate the
diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
driven by the gradient of electrochemical potential in the electrolyte
medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. \Fig{} \ref{fig:2}a) remains linear within the measurement
duration (1 h), indicating the cross-membrane concentration gradient
is almost constant during the experiment. The diffusive fluxes
correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
\Fig{} \ref{fig:2}b and Supplementary \Fig{} S2). For comparison
purposes, based on the assumption that the membrane consists
cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through the
bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table S1), the
calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
reasonable agreement with the experimental values.
